%-------------------------
% Resume in Latex
% Author : Courtney Caldwell
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/courtneyccaldwell/}{\Large Courtney C. Caldwell}} & Email : \href{mailto:courtneyccaldwell@gmail.com}{courtneyccaldwell@gmail.com}\\
  https://www.linkedin.com/in/courtneyccaldwell/ & Mobile : (617) 913-6325 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Massachusetts, Lowell}{Lowell, MA}
      {Bachelors of Science in Computer Science, General Focus;  GPA: 3.73}{Expected Dec. 2020}
   \resumeSubheading
   	{St. John's College, Annapolis}{Annapolis, MD}
	{Bachelors of Arts in Philosophy, History of Math and Science}{Graduated May 2016}
  \resumeSubHeadingListEnd
  
  %-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {University of Massachusetts, Lowell}{Lowell, MA}
      {Teaching Assistant, Artificial Intelligence}{Jan. 2020 - Present}
      \resumeItemListStart
        \resumeItem{Lead Review Sessions}
          {In charge of leading review and preparation sessions for examinations and projects.}
        \resumeItem{Curriculum Design}
        {Creating new and adjusting previous curriculum elements for an updated course plan.}
        \resumeItem{Building Course Website}
        {Responsible for the design and implementation of a new course website.}
      \resumeItemListEnd

    \resumeSubheading
      {Putnam Investments}{Andover, MA}
      {Advanced Analytics Software Developer}{Jan. 2019 - Present}
      \resumeItemListStart
        \resumeItem{Production Performance Model}
          {Researched, designed, and trained a model to take data collected on production worker performance for over 100 workers. }
        \resumeItem{Sales Prediction Model}
          {Assisted in development of a model for predicting sales based on previous touchpoint and purchase history data.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Massachusetts, Lowell}{Lowell, MA}
      {Grader, Computing I \& II}{Sep. 2018 - Dec. 2019}
      \resumeItemListStart
        \resumeItem{Grading Work}
          {Worked closely with the professor to design rubrics and graded both daily homework and exams.}
        \resumeItem{AutoGrader}
          {Designed an auto-grading script to assist in quickly assessing the quality of code submissions by students.}
      \resumeItemListEnd

    \resumeSubheading
      {S2 Security Corporation}{Framingham, MA}
      {Technical Triage Specialist}{Oct. 2016 - Jan. 2018}
      \resumeItemListStart
        \resumeItem{Workflow Automation}
          {Independently built an automated follow-up system for orders using existing API infrastructure.}
        \resumeItem{Technical Triage}
          {Provided solutions for basic programming and setup questions on over 40 products.}
        \resumeItem{Report Design}
        	 {Designed reports for over 50,000 cases through Salesforce on response times and case causes.}
      \resumeItemListEnd

%    \resumeSubheading
 %     {St. John's College}{Annapolis, MD}
  %    {Senior Laboratory Assistant}{Dec. 2015 - May 2016}
   %   \resumeItemListStart
     %   \resumeItem{Classroom Assistance}
       %   {Advised students and professors on proper laboratory experiment procedures. Taught and gave demonstrations for biology and quantum mechanics classes.}
       % \resumeItem{Laboratory Maintainence}
        %  {Maintained laboratory equipment and monitored temperature of sensitive materials and specimens.}
     % \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Skilled and Proficient In}{: Python, C, SQL}}
    \item{
    \textbf{Experience With}{: C++, R, HTML, CSS, JavaScript}
    }
    \item{
      \textbf{Technologies}{: Azure, Databricks, Jupyter, Docker, Tableau}
    }
  \resumeSubHeadingListEnd
  
  
  %-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{Game Balancing Research with Model-free Q-Learning (Python)}
  {Implemented and tested a Q-Learning based agent for testing the balance of a board game, analyzed results, and presented a paper to peers and faculty.}
    \resumeSubItem{Path Finding Agent with Probabiltiy Model Based Learning (C)}
      {Built, implemented and tested an artificial agent which found a path to a goal location in a randomly generated 2d map (represented by a 2d matrix).}
    \resumeSubItem{Productivity Performance Algorithm and Report (Python, SQL, Tableau)}
      {Algorithm designed in Python, with automatic output to Oracle SQL database, and loaded into a Tableau workbook and report.}
%    \resumeSubItem{Personal Finance Program (Python, SQL)}
%      {Program designed using Python 2.7 and SQL, created to keep track of household finances, and give spending trend data.}
  \resumeSubHeadingListEnd
  
  
  %--------EXTRACURRICULARS------------
\section{Extracurriculars}
  \resumeSubHeadingListStart
    \item{
      \textbf{Association of Computing Machinery, UML}{: V.P. (May - Dec. 2018), President (Jan. - Dec. 2019)}
      }
  \resumeSubHeadingListEnd
  
  %-----------INTERESTS-----------------
\section{Interests}
  \resumeSubHeadingListStart
    \item{
      {Gregorian Chant, Data Science, Artificial Intelligence, Machine Learning, Physics, French Translation.}
    }
  \resumeSubHeadingListEnd





%-------------------------------------------
\end{document}
